Community comparison

### 2019-12-23 code/community.Rmd
stacked barplor with cellct, 18s, rbcL inprogress

library(scatterpie)
library(ggrepel)
library(gridExtra)
library(ggthemes)
library(ggdark)
```

@@

# specify factor order
species_ord <- c("Chlainomonas A","Chlainomonas rubra", 
                "Sanguina B", "Sanguina nivaloides",
                "Chloromonas krienitzii","Chloromonas muramotoi C", "Chloromonas D", "Chloromonas cf. brevispina", "Chloromonas cf. nivalis","Chloromonas F",
                "Other Chloromonas", "Chloromonas",
                "Trebouxiophyceae G", "Trebouxiophyceae",
                "Unknown E", "Green cell", "Other")

# specify colors
plot_colors <- c(rbcl_otu_colors,s18_heat_colors, cellct_colors)

# plot
community_heatmap <- ggplot(combined, aes(x=alias %>% fct_reorder(elev_m), 
                                          y = species %>% fct_relevel(species_ord))) + 
  geom_tile(aes(alpha=rel_abund, 
                fill=species %>% fct_relevel(species_ord) )) + 
  facet_grid(rows = vars(marker %>% fct_relevel(c("Cell morphology","18S","rbcL"))), 
             scales="free_y", space="free_y") +
  scale_alpha(range = c(0.01, 1)) +
  guides(alpha="none", fill="none") +
  scale_fill_manual(values = plot_colors) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust=0.5),
        axis.title.y=element_blank()) +
  labs(x="Sample ID")

@@

>>>>

library(scatterpie)
library(ggrepel)
library(grid)
library(egg)
 library(gridExtra)
library(ggthemes)
library(ggdark)
```

@@

# specify factor order
species_ord <- c("Chlainomonas A"="#984ea3","Chlainomonas rubra"="#984ea3", #purple
                "Sanguina B"="#ff534a", "Sanguina nivaloides"="#ff534a", #red
                "Chloromonas krienitzii"="#ff7f00","Chloromonas muramotoi C"="#173416", "Chloromonas D"="#265725", "Chloromonas cf.  brevispina"="grey10", "Chloromonas cf. nivalis"="grey10","Chloromonas F"="#b25800", #greens
                "Other Chloromonas"="#4daf4a", "Chloromonas"="#4daf4a", #light greens
                "Trebouxiophyceae G"="#377eb8", "Trebouxiophyceae"="#377eb8", # blue
                "Unknown E"="grey10", "Green cell"="grey10", "Other"="grey70") #greys

# plot
community_heatmap <- ggplot(combined, aes(x=alias %>% fct_reorder(elev_m), 
                                          y = species %>% fct_relevel(names(species_ord)))) + 
  geom_tile(aes(alpha=rel_abund, 
                fill=species %>% fct_relevel(names(species_ord) ))) + 
  facet_grid(rows = vars(marker %>% fct_relevel(c("Cell morphology","18S","rbcL"))), 
             scales="free_y", space="free_y") +
  scale_alpha(range = c(0.01, 1)) +
  guides(alpha="none", fill="none") +
  scale_fill_manual(values = species_ord) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust=0.5),
        axis.title.y=element_blank()) +
  labs(x="Sample ID")

@@

```{r rotated-stacked-bar, echo=F}
# specify factor order, so Chlainomonas always on same side, etc
species_colors <- c("Chlainomonas A"="#984ea3","Chlainomonas rubra"="#984ea3", #purple
                "Sanguina B"="#ff534a", "Sanguina nivaloides"="#ff534a", #red
                "Chloromonas krienitzii"="#ff7f00","Chloromonas muramotoi C"="#173416", "Chloromonas D"="#265725", "Chloromonas cf. brevispina"="forestgreen", "Chloromonas cf. nivalis"="lightgreen","Chloromonas F"="#b25800", #greens
                "Other Chloromonas"="#4daf4a", "Chloromonas"="#4daf4a", #light greens
                "Trebouxiophyceae G"="#377eb8", "Trebouxiophyceae"="#377eb8", # blue
                "Unknown E"="grey40", "Green cell"="#b2d8b2", "Other"="grey70") #greys
# backwards
species_colors <- species_colors %>% rev()

# plot
stacked_bar <- ggplot(combined, aes(x=alias %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=species %>% fct_relevel(names(species_colors))), position="stack", stat="identity") +
  coord_flip() +
  facet_grid(cols = vars(marker %>% fct_relevel(c("Cell morphology","18S","rbcL"))), 
             scales="free_y", space="free_y") +
  theme_classic() +
  labs(x="Sample ID", y="Relative abundance")+
  scale_fill_manual(values = species_colors)

stacked_bar +
  theme(legend.position="none")
```

stacked bar legend
```{r}
legend <- stacked_bar %>% cowplot::get_legend()
grid.newpage()
grid.draw(legend)
```

dosent work in rmarkdown
```{r, echo=F}
gt <- ggplot_gtable(ggplot_build(stacked_bar))
gtable_show_layout(gt)

gt$widths[9] = 4*gt$widths[9]
grid::grid.draw(gt)
```
